Verifying Demonstrations

### 2018-10-31 paper/privacy-properties.tex

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
Receipt freeness is not \emph{always} desirable.
For instance, the participation proof might be useful to prove presence to a third party, \eg for strengthening the authenticity of witness information.
%Seb: the above sentence seems to contradict the property of coercion-resistance

@@

\sonja{new}
To contrast the difference between our context and e-voting: physical presence means support for a cause if there is only one protest. 
In case of a counterprotest, physical presence with that group means support for the counterprotest. 
In our system, it gets more ambiguous as the participants are counted if all of the following is true
\begin{enumerate*}
\item they participate in the protocol,
\item they use the protest identifier (\ie cause) for which the count is done,
\item they meet the eligibility criteria, and
\item they receive enough proof shares,
\item that are uploaded to the ledger.
\end{enumerate*}
To summarize, one could participate in a protest and be counted even when physically present at a counter-protest if the two protests are co-located and the participant chooses the corresponding cause/identifier of the original protest.

@@

The privacy properties we need in this context are the following:
\begin{description}
%Seb: while not use the term anonymity instead of unlinkability?
\item[Involuntary participant unlinkability:] \daniel{the name has a 
     double-negative ring to me} unless the participant discloses the receipt 
   (by revealing her identity), there is no link between the protest data on 
   the ledger and the identity of the participant.
%Seb: same comment as above
 \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
     too of course} unless the witness discloses the receipt (by revealing her 
   identity), there is no link between the protest data on the ledger and the 
   identity of the witness.
\end{description}
\sonja{old}
In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to her participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).

%Seb: maybe this sentence should be put before the definition of the properties
As a consequence, this leaves us with with what would correspond to vote privacy.
In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.

We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Anonymity}: participants' real (long-term) 
  identities must be unlinkable to their proofs.
\item\label{ProtestUnlink} \emph{Unlinkability}: protesters' proofs must be 
  unlinkable between protests and witnesses' proofs must be unlinkable between 
  protesters.
\end{requirements}

As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
This is, in fact, a slight increase in privacy over ordinary protests.

>>>>

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
Receipt freeness is not \emph{always} desirable.
For instance, the participation proof might be useful to prove presence to a third party, \eg for strengthening the authenticity of witness information.
%Seb: the above sentence seems to contradict the property of coercion-resistance
For instance, someone could simply physically bring Alice to a protest against her will.
Receipt freeness, while appealing at first glance, is not desirable here.
Indeed in in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{the fact that} the voter voted (\ie the protester was there), thus conflicting with verifiability.

@@

To contrast the difference between our context and e-voting: physical presence means support for a cause if there is only one protest. 
In case of a counterprotest, physical presence with that group means support for the counterprotest. 
In our system, it gets more ambiguous as the participants are counted if all of the following is true
\begin{enumerate*}
\item they participate in the protocol,
\item they use the protest identifier (\ie cause) for which the count is done,
\item they meet the eligibility criteria, and
\item they receive enough proof shares,
\item that are uploaded to the ledger.
\end{enumerate*}
To summarize, one could participate in a protest and be counted even when physically present at a counter-protest if the two protests are co-located and the participant chooses the corresponding cause/identifier of the original protest.

@@

%The privacy properties we need in this context are the following:
%\begin{description}
%%Seb: while not use the term anonymity instead of unlinkability?
%\item[Involuntary participant unlinkability:] \daniel{the name has a 
%     double-negative ring to me} unless the participant discloses the receipt 
%   (by revealing her identity), there is no link between the protest data on 
%   the ledger and the identity of the participant.
%%Seb: same comment as above
% \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
%     too of course} unless the witness discloses the receipt (by revealing her 
%   identity), there is no link between the protest data on the ledger and the 
%   identity of the witness.
%\end{description}
%\sonja{old}
In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to her participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).

%Seb: maybe this sentence should be put before the definition of the properties
As a consequence, this leaves us with with what would correspond to vote privacy.
In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
%\sonja{removed for now: For the witness, we want unlinkability between a witness's identity \(W\) and a 
%location \(l\) against an adversary who is not present in the location.
%Due to the limitations of physical space, two individuals present in the same 
%location will inevitably learn of each other's presence.
%Thus we will only try to prevent individuals who are not present to learn of 
%this presence.}
Moreover, any temporary identifiers such as pseudonyms may only be reused when strictly necessary for the fulfillment of verifiability properties listed in \label{verifiability-properties} to prevent inference on long-term identities by repeated samples and side information.

We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: each
  participant's real (long-term) identity (\(P\)) must be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters' participation proofs \(\prf_{\pid, \prtst}\) must be 
  unlinkable between protests (\(\cid, \cid' \))
\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses' participation proof shares \(\psh = (\cid, t, l, \pid,\wid)\) 
must be unlinkable between 
  protesters. (\(\pid, \pid' \))
\end{requirements}

%As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
%This is, in fact, a slight increase in privacy over ordinary protests.

### 2018-10-31 paper/protest-model.tex

%\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every weekend for the duration of a few weeks.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the cause,%
\label{CauseIsTheCommonDenominator} while the location (or area) considered 
varies over time.

For the rest of the paper, we will refer to the organizer as Alice.
Assume that the objective of Alice is to count everyone who
participated at any time and in any of the
locations~\cite{2016DemonstrationsInSeoul} %\sonja{commented out for
  %repetition: %\footnote{Note that the objective does not necessarily
              %align with the definition of the police whose interest
              %could be to determine the maximum crowd at any point in
              %time to deploy enough personnel for crowd-control.
%}.
% cause identifier
Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
More specifically, we will use the following definition.

% protest
% subprotest

@@

Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to
avoid the risk of count inflation.
Note that a participant of a protest can take the role of a protester but also act as witness for other protesters.
%Seb: the sentence below is not very clear, it should be rephrased to make it clearer
The participation proof and its proof shares are stored in a set, as
there should only be unique proof shares.

@@

The strength function \(\str\) can be used to regulate the trust in the participation count estimated.
One example would be for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
%Seb: we should define clearly the different type of witnesses (for instance unique and trusted witnesses)
Another possibility would be to also have a particular type of witness, called trusted witness, participating in the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the strength function could be defined with respect to the number of proof shares issued by trusted witnesses and set \(\theta = 1\) to require at least one proof share issued by a trusted witness.

>>>>

%\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every weekend for a few weeks duration.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the cause, \label{CauseIsTheCommonDenominator} while the location (or area) considered 
varies over time.

For the rest of the paper, we will refer to the organizer as Alice.
We assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul} %\sonja{commented out for
  %repetition: %\footnote{Note that the objective does not necessarily
              %align with the definition of the police whose interest
              %could be to determine the maximum crowd at any point in
              %time to deploy enough personnel for crowd-control.
%}.
% cause identifier
Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
More specifically, we will use the following definition.
% protest
% subprotest

@@

Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to avoid the risk of count inflation.
Note that a participant of a protest can take the role of a protester but also act as witness for other protesters.
The participation proof and its proof shares are stored as a set.
%, as there should only be unique proof shares.

@@

The strength function \(\str\) can be used to regulate the trust in the participation count estimated.
One example would be for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the strength function could be defined with respect to the number of proof shares issued by trusted witnesses.
Setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
